Versatile Robust Clustering of Ad Hoc Cognitive Radio Network

### 2016-12-04 journal-draft/bare_jrnl_comsoc.tex
modified proof

We assume the weights of sets are positive integers.
Then we will show the existence of a polynomial-time algorithm $\sigma$ which transforms any instance $\mathcal{I}$ of a weighted $k$-set packing problem, \ie a collection of sets, into a formation of clusters for a CRN.
W.l.o.g. let set $\mathcal{G} = \{ 1, \ldots , N \}$.
The polynomial algorithm $\sigma$ consists of three steps.

@@

\item In the first step, we transform the instance $\mathcal{I}$ to $\mathcal{I'}$ by duplicating the elements of the sets in $\mathcal{I}$.
In particular, as to each element in set $S\in \mathcal{I}$, we duplicate the element and assign a new index which is N bigger than the original index.
The weight of these sets remain unchanged.
The purpose of this transformation is to eliminate the set in $\mathcal{I}$, which has only one element.

\item In the second step, all the elements in $\mathcal{I'}$ are mapped to CR nodes on a two-dimensional Euclidean plane, where the CR user ID is identical with the corresponding element's index.
In particular, as to each set $S\in \mathcal{I'}$, we set up a cluster $C$ which consists of the CR users mapped from the elements in $S$, and we assign the available channels for each cluster member so that $|K(C)|$ equals to the $\omega(S)$.
The channel availability on the CR nodes whose IDs are $N$ apart is the same.
%Besides, there is a bijection between every set in $\mathcal{I'}$ and one cluster in the CRN.
%In this process, we decide the channel availability on each CR node so that the number of CCs in each cluster is equal to the weight of the corresponding set.
%
When there are two sets in $\mathcal{I'}$ and one is a subset of the other one, \ie  $S_1\subset S_2$, and $\omega(S_1) < \omega(S_2)$, then we should swap the weights of the sets before mapping them into clusters.

\item In this step, we map the elements in $\mathcal{Q}\setminus \mathcal{I}$ to CR nodes. 
We arbitrarily put these CR nodes in the CRN, then these CR nodes form singleton clusters by themselves.
According to the definition of robust clustering problem in CRN, the number of CCs of these singleton clusters is 0.
These singleton clusters and the clusters mapped from $\mathcal{I'}$ constitute a clustering solution.

@@

We have found the polynomial algorithm $\sigma$ which transforms an instance of weighted $k$-set packing to an instance of the robust clustering problem in CRN.
Assume we have a robust clustering black box which can check whether the clustering instance meets the requirement, \ie the total sum of CCs exceed $\lamda$ or not.
If \textit{yes} is said, then the total weight of the corresponding instance of the maximum weighted k-set packing problem is greater than $\lamda$.
If the black box said \textit{no},

 The direction is wrong!!
%When $\mathcal{I}$ is not an instance for weighted $k$-set packing problem due to the existence of joint sets, the corresponding clustering instance is not a successful cluster partition for the robust clustering problem, as there are overlapped clusters.
%%
%When the sets in an instance $\mathcal{I}$ for weighted $k$-set packing are disjoint, the sum of weights is identical to the total number of the CCs in the CRN which are mapped from $\mathcal{I'}$.
%Thus, when a instance $\mathcal{I}$ for $k$-set packing problem is true (or false), \ie the sum of weights is greater than $\lambda$, then in the CRN which is mapped from $\mathcal{I'}$, the sum of the numbers of CCs of the clusters is greater (or smaller) than $\lambda$.

Hence, the weighted $k$-set packing can be reduced to the robust clustering problem in CRN, then the latter problem is of NP-hard.
An example of the reduction is shown in Table~\ref{no_hard_proof_instance}.

XXXXXXXXXXXXx

\begin{table}[h!]
     \begin{center}
     \begin{tabular}{ C{3cm}  C{4.5cm} }
     \toprule
      $\mathcal{N}$  & $\{0, 1,2,3,4,5,6, 7, 8, 9\}$\\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
      $\mathcal{Q}$  & $\{ \{1\}, \{1, 5\}, \{1,2,4\}, \{2,3\}, \{4\} \}$\\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
      Instance for Weighted $k$-set packing  & $\{ \{1\}, \{2,3\}, \{4\} \}$, weights are 2, 3, 4\\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}
      Instance with dummy elements (step 1)
      & 
		$\{ \, \{1,11\},\{2,12, 3, 13\}, \{ 4,14\} \, \}$
      \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
	clusters mapped from $\mathcal{I}$  (step 2)
	  &
	  \begin{minipage}{.3\textwidth}	
      \includegraphics[width=0.6\linewidth]{np_hard_proof_step_2_3.pdf}
    \end{minipage}
          \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
	formation of clusters (step 3)
	  &
	  \begin{minipage}{.3\textwidth}	
      \includegraphics[width=0.6\linewidth]{np_hard_proof_step4.pdf}
    \end{minipage}
	  \\       \bottomrule
      \end{tabular}
      \caption{}
      \label{no_hard_proof_instance}
      \end{center}
      \end{table}

>>>>

We assume the weights of sets are positive integers.
Then we will show that any instance $\mathcal{I}$ of a weighted $k$-set packing problem, \ie a collection of sets, can be transformed to a clusters formation for a CRN.
W.l.o.g. let set $\mathcal{G} = \{ 1, \ldots , N \}$.
The polynomial algorithm $\sigma$ consists of three steps.

@@

%\item In the first step, we transform the instance $\mathcal{I}$ to $\mathcal{I'}$ by duplicating the elements of the sets in $\mathcal{I}$.
%In particular, as to each element in set $S\in \mathcal{I}$, we duplicate the element and assign a new index which is N bigger than the original index.
%The weight of these sets remain unchanged.
%The purpose of this transformation is to eliminate the set in $\mathcal{I}$, which has only one element.

\item First, the sets in the instance $\mathcal{I}$ are mapped sequentially to the clusters of CR nodes on a two-dimensional Euclidean plane, where the CR user ID is identical with the corresponding element's index.

\item Second, for each mapped cluster $C$, we assign the channels for the nodes in $C$ so that $|K(C)|$ equals to the $\omega(S)$.
We can simply assign the first $|K(C)|$ channels to each CR node in $C$, without considering the possible mismatch when the same CR node appears in different clusters and is assigned with different channels.
%The channel availability on the CR nodes whose IDs are $N$ apart is the same.
%Besides, there is a bijection between every set in $\mathcal{I'}$ and one cluster in the CRN.
%In this process, we decide the channel availability on each CR node so that the number of CCs in each cluster is equal to the weight of the corresponding set.
%
%When there are two sets in $\mathcal{I'}$ and one is a subset of the other one, \ie  $S_1\subset S_2$, and $\omega(S_1) < \omega(S_2)$, then we should swap the weights of the sets before mapping them into clusters.

%\item In second step, we map the elements in $\mathcal{Q}\setminus \mathcal{I}$ to CR nodes. 
%We arbitrarily put these CR nodes in the CRN, then these CR nodes form singleton clusters by themselves.
%According to the definition of robust clustering problem in CRN, the number of CCs of these singleton clusters is 0.
%These singleton clusters and the clusters mapped from $\mathcal{I'}$ constitute a clustering solution.

@@

\end{itemize}
The number of steps is dependent on $\mathcal{I}$, which is between 1 and $N^2$

%We have found the polynomial algorithm $\sigma$ which transforms an instance of weighted $k$-set packing to an instance of the robust clustering problem in CRN.
Assume we have a robust clustering black box which can check whether the clustering instance meets the requirement, \ie clusters are not overlapping and the total sum of CCs exceed $\lambda$ or not.
If \textit{yes} is said, then the total weight of the corresponding instance of the maximum weighted k-set packing problem is greater than $\lambda$.
If the black box said \textit{no}, either due to overlapping clusters, or the sum of CCs over all clusters is smaller than $\lambda$, the corresponding instance of the packing problem is not an solution.

% The direction is wrong!!
%When $\mathcal{I}$ is not an instance for weighted $k$-set packing problem due to the existence of joint sets, the corresponding clustering instance is not a successful cluster partition for the robust clustering problem, as there are overlapped clusters.
%%
%When the sets in an instance $\mathcal{I}$ for weighted $k$-set packing are disjoint, the sum of weights is identical to the total number of the CCs in the CRN which are mapped from $\mathcal{I'}$.
%Thus, when a instance $\mathcal{I}$ for $k$-set packing problem is true (or false), \ie the sum of weights is greater than $\lambda$, then in the CRN which is mapped from $\mathcal{I'}$, the sum of the numbers of CCs of the clusters is greater (or smaller) than $\lambda$.

Hence, the weighted $k$-set packing can be reduced to the robust clustering problem in CRN, then the latter problem is of NP-hard.
%An example of the reduction is shown in Table~\ref{no_hard_proof_instance}.

%\begin{table}[h!]
%     \begin{center}
%     \begin{tabular}{ C{3cm}  C{4.5cm} }
%     \toprule
%      $\mathcal{N}$  & $\{0, 1,2,3,4,5,6, 7, 8, 9\}$\\ 
%    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
%      $\mathcal{Q}$  & $\{ \{1\}, \{1, 5\}, \{1,2,4\}, \{2,3\}, \{4\} \}$\\ 
%    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
%      Instance for Weighted $k$-set packing  & $\{ \{1\}, \{2,3\}, \{4\} \}$, weights are 2, 3, 4\\ 
%    \cmidrule(r){1-1}\cmidrule(lr){2-2}
%      Instance with dummy elements (step 1)
%      & 
%		$\{ \, \{1,11\},\{2,12, 3, 13\}, \{ 4,14\} \, \}$
%      \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
%	clusters mapped from $\mathcal{I}$  (step 2)
%	  &
%	  \begin{minipage}{.3\textwidth}	
%      \includegraphics[width=0.6\linewidth]{np_hard_proof_step_2_3.pdf}
%    \end{minipage}
%          \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
%	formation of clusters (step 3)
%	  &
%	  \begin{minipage}{.3\textwidth}	
%      \includegraphics[width=0.6\linewidth]{np_hard_proof_step4.pdf}
%    \end{minipage}
%	  \\       \bottomrule
%      \end{tabular}
%      \caption{}
%      \label{no_hard_proof_instance}
%      \end{center}
%      \end{table}
